Endogenous Politics and \\ the Design of Trade Institutions

### 2017-03-03 intro.tex
add costly state verification reference
add reference to Cole, Lake and Zissimos

We miss important dynamics like this one when we assume political pressure is exogenous as is done for tractability in almost all the literature that studies trading rules and institutions (see \Textcite{mrc2007} and \Textcite{lt} for notable exceptions). The main contribution of this paper is to provide a tractable framework for integrating lobbying incentives into these analyses. This framework can be used to study a wide range of questions, including dispute settlement design, optimal retaliation schemes and depth of integration among others. It's well-positioned to examine the interactions between exogenous shocks and lobbying incentives and will be useful for shedding light on questions surrounding how governments choose among protective measures over time.

@@

On escape clauses, \Textcite{bs1990} is similar in spirit to \Textcite{bs2005}. Here, there is no private information and trade volume shocks in the presence of self-enforcement constraints are behind the need for an escape clause. \Textcite{bc} find empirical support for this theory. \Textcite{beshkar2010b} compares the GATT escape clause to the WTO Safeguards agreement and shows that the Dispute Settlement Body as a non-binding arbitrator can assist governments in self-enforcing their trade agreements.

>>>>

We miss important dynamics like this one when we assume political pressure is exogenous as is done for tractability in almost all the literature that studies trading rules and institutions (see \Textcite{mrc2007}, \Textcite{lt} and \Textcite{buzard2013a} for exceptions).\footnote{\Textcite{clz} also endogenize lobbying using a new approach, that of a contest model.} The main contribution of this paper is to provide a tractable framework for integrating lobbying incentives into these analyses. This framework can be used to study a wide range of questions, including dispute settlement design, optimal retaliation schemes and depth of integration among others. It's well-positioned to examine the interactions between exogenous shocks and lobbying incentives and will be useful for shedding light on questions surrounding how governments choose among protective measures over time.

@@

On escape clauses, \Textcite{bs1990} is similar in spirit to \Textcite{bs2005}. Here, there is no private information and trade volume shocks in the presence of self-enforcement constraints are behind the need for an escape clause. \Textcite{bc} find empirical support for this theory. \Textcite{beshkar2010b} compares the GATT escape clause to the WTO Safeguards agreement and shows that the Dispute Settlement Body as a non-binding arbitrator can assist governments in self-enforcing their trade agreements. \Textcite{ms2012a} study the optimal form of the trade agreement in the presence of renegotiation where compensation between governments is inefficient.
